### 2023-02-10 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_interpreting_probabilities@eb3049b5587cebcac0a700128f22895c74428da6 🚀

As opposed to metawebs, probabilistic local food webs represent the
likelihood that two species will interact at a specific location and
within a given time period; in other words, they are context dependant.
To be specific, space is defined here as the geographic coordinates \$
\bold x, \bold y\$ of the spatial boundaries delineating the system,
whereas time is the time interval (\$ \bold t\$) during which
interactions were sampled or for which they were predicted. We put these
variables in bold to emphasize that they are not single values, but
rather continued dimensions that could be outlined differently depending
on the study system. Regardless of how they were defined, they always
delineate a specific area \(A\) and duration \(D\). These could refer to
the sampled area and duration or to the targeted location and time
period.

>>>>

As opposed to metawebs, probabilistic local food webs represent the
likelihood that two species will interact at a specific location and
within a given time period; in other words, they are context dependant.
To be specific, space is defined here as the geographic coordinates \$
\bold x, \bold y\$ of the spatial boundaries delineating the system,
whereas time is the time interval \$ \bold t\$ during which interactions
were sampled or for which they were predicted. We put these variables in
bold to emphasize that they are not single values, but rather continued
dimensions that could be outlined differently depending on the study
system. Regardless of how they were defined, they always delineate a
specific area \(A\) and duration \(D\). These could refer to the sampled
area and duration or to the targeted location and time period.
